\textbf{Real-time guitar transcription using\\Fourier transform based methods}\\A pitch estimation framework and overtone sieve algorithm

### 2021-05-05 paper.tex
pseudo code

@@

\usepackage[english]{babel}
\usepackage[stretch=10, shrink=10]{microtype}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{float}

@@

@@

@@

The Gaussian average envelope is calculated for every Fourier bin $i$ by taking the weighted average of a arbitrary number of bins around $i$. The weights are determined by a Gaussian function ($e^{-\pi(\frac{x}{\sigma})^2}$). The value of $\sigma$ and number of bins around $i$ can be changed in \texttt{config.h}. Higher values for $\sigma$ makes points around the considered point have a higher weighting. In our implementation, $\sigma$ is set to 1.2 and the number of bins is set to 47.

>>>>

% Pseudo-code
% Contributie exacter verwoorden (abstract en einde introduction)

@@

\usepackage[english]{babel}
\usepackage[stretch=10, shrink=10]{microtype}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{float}
\usepackage[linesnumbered,lined,commentsnumbered]{algorithm2e}

@@

An pseudo-code overview of the transcription process is given in Algorithm~\ref{alg:overview}.
\input{overview.pc}

@@

Because our input data is purely real, we know the output of the Fourier transform will be symmetric. For this reason, we can omit calculation half of the output. This results in an almost two times speed-up\cite{twotimes}.

@@

The Gaussian average envelope is calculated for every Fourier bin $i$ by taking the weighted average of a arbitrary number of bins around $i$. The weights are determined by a Gaussian function ($e^{-\pi(\frac{x}{\sigma})^2}$). The value of $\sigma$ and number of bins around $i$ can be changed in \texttt{config.h}. Higher values for $\sigma$ makes points around the considered point have a higher weighting. In our implementation, $\sigma$ is set to 1.2 and the number of bins is set to 47. In Algorithm~\ref{alg:gauss} and~\ref{alg:env}, a pseudo-code implementation is given for calculating the Gaussian weights and calculating the envelope based on these weights.
\input{gauss.pc}
\input{env.pc}
